*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-08 Code/Manuscript_O2.Rmd
Added ANOVA blurb. Fixed  1 reference to a figure

We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to compare growth response between 660 nm (red) and 450 nm (blue) growth light and additionally, to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across pooled photoperiod data. 
To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when the p value was < 0.05.

@@

The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR. Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G), with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).  MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I), with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).

>>>>

We performed one-way ANOVA to examine statistical differences between Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red light) and 450 nm (blue light) growth data for each combination of strain and [O~2~]. We also performed one-way ANOVA to examine statistical differences between Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to each photoperiod (4 h, 8 h, 12 h, 16 h) and pooled photoperiod growth data for each combination of strain and [O~2~]. Photoperiod growth data that showed complete growth inhibition for each combination of strain, [O~2~] and imposed spectral waveband were omitted from the pooled photoperiod model. Statistical differences were determined at p < 0.05.

@@

The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR. Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau, with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).  MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
